A review of Crime data and how GDP affects Crime Rates

### 2017-03-08 paper/paper.Rmd
add tex file

---
title: "Final Project Paper"
output:
  html_document: default
  html_notebook: default
---

@@

********** Marisa
The key findings of our research showed that a poisson regression showed no correlation between the GDP per person and crime per person in each metropolitan area with population as another independent variable. Between all of the years from 2010 to 2015, there was no significance between GDP per person, crime per person, and population of a metropolitan area for any compared years. From this, our contribution to society and information in general is that just looking at a metropolitan area's economy and population is not a good determining factor on the number of crimes permitted by person.

>>>>

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: ~\Documents\INFO370\info370-final\paper\svm-latex-ms.tex
title: "A review of Crime data and how GDP affects Crime Rates"
author:
- name: Kai Yoshino
  affiliation: Univeristy of Washington
- name: Isabella Spaletta 
  affiliation: University of Washington
- name: Chrisopther Ross
  affiliation: University of Washington
-
abstract: "The relationship between crime and the economy is complex. By analyzing the connection between crimes committed, GDP, and populations of metropolitan areas from the years 2010 to 2015, we seek to gain a deeper understanding on the driving forces behind these societal elements. The key findings of our research revealed that with a Poisson regression, there's no significant correlation between the count of total crimes committed per person (crime rate) in a metropolitan area and the predictors of that area's GDP per person or population. However, analyzing the rate changes in each variable via linear regression shows the opposite: a significant correlation. Looking at changes in both property and violent crime rates, we also found a significant correlation to both GDP rate changes and population changes. From this, our contribution to criminology and economics demonstrates that analyzing a metropolitan area's economy and population only scratches the surface for determining crime counts, suggesting that focus should be veered towards analyzing the rate changes in each variable. "
keywords: "Crime, GDP, Poisson Regression, Linear Regression"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 11pt
# spacing: double
#bibliography: ~/Dropbox/master.bib
#biblio-style: apsr
---

@@

********** Marisa
